Clustering/Orthofinder analysis

### 2022-03-08 analysis/Orthofinder.Rmd
Add files

# FINAL version redoing - terrestrial vs aquatics vs seagrasses

@@

MUCH better. The biggest chunk of orthogroups is not in aquatics or seagrasses with 13562 orthogroups. 3845 orthogroups are in duckweeds, seagrasses, terrestrials, but not algae - 2217 orthogroups are unique in seagrasses.

>>>>

# FINAL version redoing - terrestrial vs duckweeds vs algae vs seagrasses

@@

MUCH better. The biggest chunk of orthogroups is only in terrestrials with 13562 orthogroups. 3845 orthogroups are in duckweeds, seagrasses, terrestrials, but not algae - 2217 orthogroups are unique in seagrasses.
